### 2025-05-08 introduction.tex
final draft
new

Advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable for risk assessment of such products.
In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model tail risk with a rule-based design.
~\cite{glasserman2004monte} provide a comprehensive overview of Monte Carlo simulation methods in financial engineering and risk management applications.

@@

A standard nested simulation procedure consists of two levels of simulation: the outer-level simulation generates the underlying risk factors, while the inner-level simulation estimates the value of interest with the inner sample mean from another level of Monte Carlo simulation.

@@

Risk management of VAs is a challenging problem due to the complex interactions between the policyholder's behavior and the financial market dynamics.

@@

\section{Risk Management of Variable Annuities with Nested Simulation}

\gls{va} contracts are index-linked insurance products that offer policyholders the upside potential of equity markets while providing guarantees against downside risk.
These products have gained a substantial amount of interest as they address the needs of individuals seeking both wealth accumulation and financial security, especially in the context of retirement planning.
The key feature of VAs is their embedded guarantees, which ensure a specified minimum benefit regardless of market performance.
Two \gls{va} contracts that are most relevant to this thesis are \gls{gmmb} and \gls{gmwb}.
The \gls{gmmb} guarantees that at the maturity of the contract, the policyholder will receive no less than the initial investment or a predetermined minimum amount.
The \gls{gmwb} allows policyholders to withdraw a specified percentage of their benefit base each period during the contract horizon~\citep{hardy2003investment}.
While these guarantees make VAs more attractive to consumers by offering protection against market downturns and ensuring income stability, they also introduce significant financial risks for insurers.
The embedded options within \gls{gmmb} and \gls{gmwb} expose insurers to market risk, longevity risk, and policyholder behavior risk.
Therefore, an effective management of these risks is crucial for insurers to maintain solvency and meet regulatory capital requirements.

One of the primary risk management strategies employed by insurers to mitigate the financial risks associated with VAs is dynamic hedging.
Dynamic hedging involves frequent adjustments to a portfolio of financial instruments to offset changes in guarantee values due to market movements~\citep{hull2016options}.
This strategy aims to neutralize the insurer's liability sensitivity to market fluctuations by constructing a hedging portfolio that replicates the guarantees' cash flows.
However, dynamic hedging introduces complexity in estimating the insurer's overall risk exposure.
One such example is the estimation of tail risk measures of a \gls{va} contract.
It requires a stochastic modeling of the financial market and an accurate loss estimation of the hedging portfolio under different market scenarios.
Nested simulation is a robust method for estimating risk measures in complex settings~\citep{gordy2010nested}.
In nested simulation, an outer simulation generates a set of market scenarios over the contract horizon, while an inner simulation estimates the contract loss in each scenario.
By combining the results of the inner simulations across the outer scenarios, nested simulation provides an accurate estimate of the tail risk of the \gls{va} contract.

@@

Metamodeling, or surrogate modeling, approximates complex simulation models with simpler, computationally efficient models.
In Monte Carlo simulations, metamodels reduce computational costs by approximating simulation outputs based on input variables~\citep{kleijnen2018design}.
This section introduces metamodeling for a Monte Carlo simulation, elaborates on its methodologies, and highlights its importance in practical applications.

Monte Carlo simulations are widely used for modeling and analyzing complex systems that are probabilistic in nature.
These simulations often require a substantial amount of computational resources, especially when a high degree of accuracy or a high number of iterations is necessary~\citep{glasserman2004monte}.
Metamodeling addresses this challenge by constructing an approximate model (known as a metamodel) that emulates the behavior of the original simulation model with much less computational effort.
The metamodel serves as a predictive model that maps input variables to output responses.
Learning from a set of simulation runs, the metamodel can generalize and predict outputs for new inputs without running the full simulation.
Metamodeling is especially useful for computationally expensive simulation models.
Replacing the simulation model with a metamodel significantly reduces computational costs.
This allows for faster convergence of simulation-based estimators.

@@

The development of advanced machine learning models and deep learning techniques has enhanced metamodeling approaches for Monte Carlo simulations, especially in high-dimensional and complex problem settings.
Examples of machine learning applications include~\cite{jin2020deep},~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might struggle to model effectively.
In the following sections, we discuss machine learning algorithms in the context of metamodeling for Monte Carlo simulations and their applications in risk management.

@@

\begin{equation}
    f(x; \theta) = f^{(k)}(f^{(k-1)} \cdots (f^{(2)}(f^{(1)}(x;\theta^{(1)});\theta^{(2)} )\cdots ;\theta^{(k-1)});\theta^{(k)}),
\end{equation}
where $\theta = (\theta^{(1)}, \theta^{(2)}, \ldots, \theta^{(k)})$ are trainable parameters of the neural network, $f^{(i)}$ is an $i$-th layer of the neural network, $x$ is an input feature vector, $f^{(1)}(x;\theta^{(1)}) = x$, $f^{(k)}$ is an output layer, $k$ is a number of layers, and $f^{(i)}$ is an output of the $i$-th layer.
To transition from layer $i-1$ to layer $i$,
\begin{equation} \label{eq:neural}
    f^{(i)}(z;\theta^{(i)}) = a^{(i)}(\beta_0^{(i)} + \sum_{j=1}^{p_i} \beta_j^{(i)} z),
\end{equation}
where $a^{(i)}$ are nonlinear activation functions, $\theta^{(i)} = (\beta_0^{(i)}, \dots, \beta_p^{(i)})$ are trainable parameters of the $i$-th layer, and $p_i$ is a number of neurons in the previous layer.
Equation~\eqref{eq:neural} represents a single neuron in a neural network, which applies a linear transformation to the input followed by a non-linear activation function.
The linear transformation is similar to the linear regression model in Equation~\eqref{eq:regression}, but the non-linear activation function allows the neural network to model complex, non-linear relationships in the data.
The \gls{fnn} is tuned by adjusting the trainable parameters $\theta$ while fixing the activation functions $a^{(i)}$.
A typical choice for the activation function is the \gls{relu}, which is defined as $a(z) = \max(0, z)$~\citep{nair2010rectified}.
The activation function choice is crucial for training neural networks.
While sigmoid and hyperbolic tangent functions were popular in early neural networks, ReLU has become the default activation function for deep networks due to its ability to mitigate the vanishing gradient problem and promote sparse activations~\citep{lecun2015deep}.

@@

The most well-known theorem in neural network theory is the universal approximation theorem~\citep{hornik1989multilayer}.
It states that given appropriate activation functions $a$, a feedforward neural network with a single hidden layer containing a finite number of neurons can approximate any continuous function on a compact subset of $\mathbb{R}^n$ to arbitrary accuracy.
Despite this theoretical guarantee for single-layer neural networks, in practice, \gls{dnn} with multiple hidden layers have been shown to be more effective at capturing complex patterns and relationships in data~\citep{lecun2015deep}.
Examples include AlexNet~\citep{krizhevsky2012imagenet}, VGG~\citep{simonyan2014very}, and ResNet~\citep{he2016deep}, which have achieved state-of-the-art performance on image classification tasks.
In this thesis, we focus on the application of deep neural networks, specifically \gls{lstm}, as metamodels for nested simulation procedures in risk management applications.

@@

To overcome the limitations of \gls{fnn}s in handling sequential input, \gls{rnn}s were introduced.
In an \gls{rnn}, the hidden state at each time step is a function of both the current input and the hidden state from the previous time period~\citep{elman1990finding}:

\begin{equation}
    h_t = f(x_t, h_{t-1}; \theta),
\end{equation}
where $h_t$ is the hidden state at time $t$, $x_t$ is the input at time $t$, $h_{t-1}$ is the hidden state at time $t-1$, and $f$ is the recurrent function parameterized by $\theta$.
This architecture enables \gls{rnn} to capture temporal dependencies by maintaining a dynamic internal state that reflects the memory of past inputs.
However, traditional \gls{rnn} suffer from the vanishing and exploding gradient problem, which hinders their ability to capture longer-term dependencies that often present in financial time series~\citep{bengio1994learning}.
During training, gradients propagated backward through time can either diminish exponentially (known as vanishing gradients) or grow uncontrollably (known as exploding gradients).
This limitation is particularly problematic in modeling long-term financial contracts and insurance guarantees, where patterns may span over extended periods.

To address these issues, a \gls{lstm} network was developed by~\citet{hochreiter1997long}.
It is a specialized form of RNNs designed to capture long-term dependencies more effectively with the help of \gls{rnn} memory cells and gating mechanisms.

\begin{align*}
    i_t &= a(W_i x_t + U_i h_{t-1} + b_i), \\
    f_t &= a(W_f x_t + U_f h_{t-1} + b_f), \\
    o_t &= a(W_o x_t + U_o h_{t-1} + b_o), \\
    g_t &= a(W_g x_t + U_g h_{t-1} + b_g), \\
    c_t &= f_t \odot c_{t-1} + i_t \odot g_t, \\
    h_t &= o_t \odot \tanh(c_t),
\end{align*}
where $i_t, f_t, o_t, g_t, c_t, h_t$ are an input gate, a forget gate, an output gate, a cell input, a cell state, and a hidden state at time $t$, respectively.
$W_i$, $W_f$, $W_o$, $W_g$, $U_i$, $U_f$, $U_o$, $U_g$ are weight matrices, and $b_i$, $b_f$, $b_o$, $b_g$ are bias vectors.
$a$ is the activation function, typically the sigmoid function, and $\odot$ denotes element-wise multiplication.

@@

However, the training of neural networks is non-convex, and the optimization problem is challenging.
\gls{sgd} is a popular optimization algorithm for training neural networks.
It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than a crude gradient descent.
However, \gls{sgd} may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
To address these issues, various adaptive learning rate methods have been proposed in the literature.
The most popular approach is Adam optimizer, which is an SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.

>>>>

Advanced \gls{mc} simulation techniques, particularly nested simulation procedures, become indispensable for risk assessment of such products.
In contrast to finite-difference methods, a \gls{mc} simulation scheme is more flexible and can be easily adapted to model tail risk with a rule-based design. ~\cite{glasserman2004monte} provide a comprehensive overview of \gls{mc} simulation methods in financial engineering and risk management applications.

@@

A standard nested simulation procedure consists of two levels of simulation: the outer-level simulation generates the underlying risk factors, while the inner-level simulation estimates the value of interest with the inner sample mean from another level of \gls{mc} simulation.

@@

Risk management of \gls{va} contracts is a challenging problem due to the complex interactions between the policyholder's behavior and the financial market dynamics.

@@

\section{Risk Management of VAs with Nested Simulation}

\gls{va} contracts are index-linked insurance products that offer policyholders the upside potential of equity markets while providing guarantees against downside risk.
These products have gained a substantial amount of interest as they address the needs of individuals seeking both wealth accumulation and financial security, especially in the context of retirement planning.
The key feature of \gls{va} contracts is their embedded guarantees, which ensure a specified minimum benefit regardless of market performance.
Two \gls{va} contracts that are most relevant to this thesis are \gls{gmmb} and \gls{gmwb}.
The \gls{gmmb} guarantees that at the maturity of the contract, the policyholder will receive no less than the initial investment or a predetermined minimum amount.
The \gls{gmwb} allows policyholders to withdraw a specified percentage of their benefit base each period during the contract horizon~\citep{hardy2003investment}.
While these guarantees make \gls{va} contracts more attractive to consumers by offering protection against market downturns and ensuring income stability, they also introduce significant financial risks for insurers.
The embedded options within \gls{gmmb} and \gls{gmwb} expose insurers to market risk, longevity risk, and policyholder behavior risk.
Therefore, an effective management of these risks is crucial for insurers to maintain solvency and meet regulatory capital requirements.

One of the primary risk management strategies employed by insurers to mitigate the financial risks associated with \gls{va} contracts is dynamic hedging.
Dynamic hedging involves frequent adjustments to a portfolio of financial instruments to offset changes in guarantee values due to market movements~\citep{hull2016options}.
This strategy aims to neutralize the insurer's liability sensitivity to market fluctuations by constructing a hedging portfolio that replicates the guarantees' cash flows.
However, dynamic hedging introduces complexity in estimating the insurer's overall risk exposure.
One such example is the estimation of tail risk measures of a \gls{va} contract.
It requires a stochastic modeling of the financial market and an accurate loss estimation of the hedging portfolio under different market scenarios.
Nested simulation is a robust method for estimating risk measures in complex settings~\citep{gordy2010nested}.
In nested simulation, an outer simulation generates a set of market scenarios over the contract horizon, while an inner simulation estimates the contract loss in each scenario.
By combining the results of the inner simulations across the outer scenarios, nested simulation provides an accurate estimate of the tail risk of the \gls{va} contract.

@@

Metamodeling, or surrogate modeling, approximates complex simulation models with simpler, computationally efficient models.
In \gls{mc} simulations, metamodels reduce computational costs by approximating simulation outputs based on input variables~\citep{kleijnen2018design}.
This section introduces metamodeling for a \gls{mc} simulation, elaborates on its methodologies, and highlights its importance in practical applications.

\gls{mc} simulations are widely used for modeling and analyzing complex systems that are probabilistic in nature.
These simulations often require a substantial amount of computational resources, especially when a high degree of accuracy or a high number of iterations is necessary~\citep{glasserman2004monte}.
Metamodeling addresses this challenge by constructing an approximate model (known as a metamodel) that emulates the behavior of the original simulation model with much less computational effort.
The metamodel serves as a predictive model that maps input variables to output responses.
Learning from a set of simulation runs, the metamodel can generalize and predict outputs for new inputs without running the full simulation.
Metamodeling is especially useful for computationally expensive simulation models.
Replacing the simulation model with a metamodel significantly reduces computational costs.
This allows for faster convergence of simulation-based estimators.

@@

The development of advanced machine learning models and deep learning techniques has enhanced metamodeling approaches for \gls{mc} simulations, especially in high-dimensional and complex problem settings.
Examples of machine learning applications include~\cite{jin2020deep},~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might struggle to model effectively.
In the following sections, we discuss machine learning algorithms in the context of metamodeling for \gls{mc} simulations and their applications in risk management.

@@

\begin{equation} \label{eq:fnn}
    f(x; \theta) = f^{(k)}(f^{(k-1)} \cdots (f^{(2)}(f^{(1)}(x;\theta^{(1)});\theta^{(2)} )\cdots ;\theta^{(k-1)});\theta^{(k)}),
\end{equation}
where $\theta = (\theta^{(1)}, \theta^{(2)}, \ldots, \theta^{(k)})$ are trainable parameters of the neural network, $f^{(i)}$ is an $i$-th layer of the neural network, $x$ is an input feature vector, $f^{(1)}(x;\theta^{(1)}) = x$, $f^{(k)}$ is an output layer, $k$ is a number of layers, and $f^{(i)}$ is an output of the $i$-th layer.
To transition from layer $i-1$ to layer $i$,
\begin{equation} \label{eq:neural}
    f^{(i)}(z;\theta^{(i)}) = a^{(i)}(\beta_0^{(i)} + \sum_{j=1}^{p_i} \beta_j^{(i)} z),
\end{equation}
where $a^{(i)}$ are nonlinear activation functions, $\theta^{(i)} = (\beta_0^{(i)}, \dots, \beta_p^{(i)})$ are trainable parameters of the $i$-th layer, and $p_i$ is a number of neurons in the previous layer.
Equation~\eqref{eq:neural} represents a single neuron in a neural network, which applies a linear transformation to the input followed by a non-linear activation function.
The linear transformation is similar to the linear regression model in Equation~\eqref{eq:regression}, but the non-linear activation function allows the neural network to model complex, non-linear relationships in the data.
The \gls{fnn} is tuned by adjusting the trainable parameters $\theta$ while fixing the activation functions $a^{(i)}$.
A typical choice for the activation function is the \gls{relu}, which is defined as $a(z) = \max(0, z)$~\citep{nair2010rectified}.
The activation function choice is crucial for training neural networks.
While sigmoid and hyperbolic tangent functions were popular in early neural networks, ReLU has become the default activation function for deep networks due to its ability to mitigate the vanishing gradient problem and promote sparse activations~\citep{lecun2015deep}.

@@

The most well-known theorem in neural network theory is the universal approximation theorem~\citep{hornik1989multilayer}.
It states that given appropriate activation functions $a$, a feedforward neural network with a single hidden layer containing a finite number of neurons can approximate any continuous function on a compact subset of $\mathbb{R}^n$ to arbitrary accuracy.
Despite this theoretical guarantee for single-layer neural networks, in practice, \gls{dnn} with multiple hidden layers have been shown to be more effective at capturing complex patterns and relationships in data~\citep{lecun2015deep}.
Examples include AlexNet~\citep{krizhevsky2012imagenet}, Visual Geometic Group~\citep{simonyan2014very}, and ResNet~\citep{he2016deep}, which have achieved state-of-the-art performance on image classification tasks.
In this thesis, we focus on the application of deep neural networks, specifically \gls{lstm}, as metamodels for nested simulation procedures in risk management applications.

@@

To overcome the limitations of \gls{fnn}s in handling sequential input, A \gls{rnn} was introduced.
In an \gls{rnn}, the hidden state at each time step is a function of both the current input and the hidden state from the previous time period~\citep{elman1990finding}:

\begin{equation} \label{eq:rnn}
    h_t = f(x_t, h_{t-1}; \theta),
\end{equation}
where $h_t$ is the hidden state at time $t$, $x_t$ is the input at time $t$, $h_{t-1}$ is the hidden state at time $t-1$, and $f$ is the recurrent function parameterized by $\theta$.
This architecture enables \gls{rnn} to capture temporal dependencies by maintaining a dynamic internal state that reflects the memory of past inputs.
However, traditional \gls{rnn} suffer from the vanishing and exploding gradient problem, which hinders their ability to capture longer-term dependencies that often present in financial time series~\citep{bengio1994learning}.
During training, gradients propagated backward through time can either diminish exponentially (known as vanishing gradients) or grow uncontrollably (known as exploding gradients).
This limitation is particularly problematic in modeling long-term financial contracts and insurance guarantees, where patterns may span over extended periods.

To address these issues, a \gls{lstm} network was developed by~\citet{hochreiter1997long}.
It is a specialized form of \gls{rnn}s designed to capture long-term dependencies more effectively with the help of \gls{rnn} memory cells and gating mechanisms.

\begin{align} \label{eq:lstm}
    i_t &= a(W_i x_t + U_i h_{t-1} + b_i), \nonumber \\
    f_t &= a(W_f x_t + U_f h_{t-1} + b_f), \nonumber \\
    o_t &= a(W_o x_t + U_o h_{t-1} + b_o), \nonumber \\
    g_t &= a(W_g x_t + U_g h_{t-1} + b_g), \nonumber \\
    c_t &= f_t \odot c_{t-1} + i_t \odot g_t, \nonumber \\
    h_t &= o_t \odot \tanh(c_t),
\end{align}
where $i_t, f_t, o_t, g_t, c_t, h_t$ are an input gate, a forget gate, an output gate, a cell input, a cell state, and a hidden state at time $t$, respectively.
$W_i$, $W_f$, $W_o$, $W_g$, $U_i$, $U_f$, $U_o$, $U_g$ are weight matrices, and $b_i$, $b_f$, $b_o$, $b_g$ are bias vectors.
$a$ is the activation function, typically the sigmoid function, and $\odot$ denotes an element-wise multiplication.

@@

However, the training of neural networks is non-convex, and the optimization problem is challenging.
\gls{sgd} is a popular optimization algorithm for training neural networks.
It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than a crude gradient descent.
However, \gls{sgd} may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
To address these issues, various adaptive learning rate methods have been proposed in the literature.
The most popular approach is the Adam optimizer, which is an \gls{sgd} algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.

### 2025-05-08 project1/nsSurvey.tex
new

\begin{enumerate}
    \item   Nested expectation form:
            \begin{equation*}
                \hat{\rho}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}_{N, i}) = \frac{1}{M} \sum_{i=1}^M h(\bar{Y}_{N, i}), \quad X_i \sim F_X.
            \end{equation*}
    \item   Value at risk (\gls{var}):
            \begin{equation*}
                \hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)}.
            \end{equation*}

@@

Supervised learning-based nested simulation procedures treat the inner simulation model $L(\cdot)$ as a black-box function, and they approximate $L(\cdot)$ with supervised learning metamodels.
In this metamodeling approach, $L(\cdot)$ can be approximated by $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, which is based on a family of chosen function and observations from the standard nested simulation procedure.
Consider the observation pairs $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$ as training data.
We can use supervised learning to approximate $L_i$ by $\hat{L}_{M, N}^{\text{SL}}(X_i)$ and to pool the inner replications from all outer scenarios.
Specifically, $\hat{L}^{\text{SL}}{M, N}(\cdot)$ denotes a supervised learning model trained on $(X_i, \hat{L}{N, i})$ for $i \in {1, \dots, M}$.
This is the output of the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
To evaluate the convergence of the supervised learning-based nested simulation procedure, we consider the convergence behavior of the supervised learning model $h(\hat{L}^{\text{SL}}_{M, N}(\cdot))$ to the true risk measure $\rho = h(L(\cdot))$.
More specifically, we want to study the following quantity
\begin{equation}\label{eq1:sl-E}
    \mathbb{E} \left[ h(\hat{L}^{\text{SL}}_{M, N}(X))   \right] - \rho, \quad X \sim F_X.
\end{equation}

@@

\section{Conclusion and Extensions}\label{sec1:conclusion}
In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a metamodel. 
In this study, we review the literature on nested simulation procedures in financial engineering and provide fair comparisons of different metamodels by using the same set of numerical examples. 
Asymptotic properties of estimators for different nested simulation procedures are influenced by their corresponding metamodels.
To show an asymptotic convergence result, a more complex metamodels requires a more stringent set of assumptions on the distribution of the outer scenario and the inner simulation noise.
In terms of finite-sample behavior, this study provides a comprehensive comparison of different nested simulation procedures, and the findings can be used to guide the choice of a proper nested simulation procedure for a given nested estimation problem.
With extensive numerical experiments, we have found that the finite-sample performance of a procedure can deviate from its theory. 
In theory, supervised learning-based nested simulation procedures often provide higher rates of convergence, but they come at the computational expense of model training and generating predictions from the trained models. 
The likelihood ratio-based procedure requires no training, but it is expensive to compute, and it is also expensive to store the likelihood weights.
As a result, the total computational budget is not necessarily the same as the simulation budget, which is usually a limiting factor for practical applications.
A kernel-based procedure, e.g., \gls{knn} and \gls{var}, requires cross-validation, and its empirical performance depends heavily on the choice of hyperparameters.
A \gls{knn}-based procedure is sensitive to the asset dimension and the problem complexity.
A \gls{krr}-based procedure is computationally expensive, and its cost grows quickly with the simulation budget.
For kernel-based procedures, the computational cost is heavily dependent on the efficient implementation of the associated algorithms.
For a nested estimation problem with a given computational budget, we suggest the use of the regression-based simulation procedure when the budget size is moderate. 
It is efficient to implement, and it exhibits fast empirical convergence in estimating risk measures for popular option portfolios. 
However, we have only examined the performance for option portfolios in this study, where finding a suitable set of basis functions for regression is relatively easy.
In practice, a variable annuity contract is often high-dimensional in time with a complex payoff structure, and it is a challenging problem for nested simulation procedures.
The time dependence in the feature space leads to multi-collinearity, and the regression-based procedure may not be the best choice in such instances.
In such cases, a neural network-based procedure may be more suitable, as it is a data-driven algorithm that finds a suitable set of basis functions automatically.
In Chapter~\ref{chap:project2}, we examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for variable annuities.

>>>>

\begin{enumerate}
    \item   Nested expectation form:
            \begin{equation*}
                \hat{\rho}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}_{N, i}) = \frac{1}{M} \sum_{i=1}^M h(\bar{Y}_{N, i}), \quad X_i \sim F_X.
            \end{equation*}
    \item   \gls{var}:
            \begin{equation*}
                \hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)}.
            \end{equation*}

@@

Supervised learning-based nested simulation procedures treat the inner simulation model $L(\cdot)$ as a black-box function, and they approximate $L(\cdot)$ with supervised learning metamodels.
In this metamodeling approach, $L(\cdot)$ can be approximated by $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, which is based on a family of chosen function and observations from the standard nested simulation procedure.
Consider the observation pairs $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$ as training data.
We can use supervised learning to approximate $L_i$ by $\hat{L}_{M, N}^{\text{SL}}(X_i)$ and to pool the inner replications from all outer scenarios.
Specifically, $\hat{L}^{\text{SL}}{M, N}(\cdot)$ denotes a supervised learning model trained on $(X_i, \hat{L}_{N, i})$ for $i \in {1, \dots, M}$.
This is the output of the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications.
To evaluate the convergence of the supervised learning-based nested simulation procedure, we consider the convergence behavior of the supervised learning model $h(\hat{L}^{\text{SL}}_{M, N}(\cdot))$ to the true risk measure $\rho = h(L(\cdot))$.
More specifically, we want to study the following quantity
\begin{equation}\label{eq1:sl-E}
    \mathbb{E} \left[ h(\hat{L}^{\text{SL}}_{M, N}(X))   \right] - \rho, \quad X \sim F_X.
\end{equation}

@@

\section{Conclusion and Extensions}\label{sec1:conclusion}
In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a metamodel. 
In this study, we review the literature on nested simulation procedures in financial engineering and provide fair comparisons of different metamodels by using the same set of numerical examples. 
Asymptotic properties of estimators for different nested simulation procedures are influenced by their corresponding metamodels.
To show an asymptotic convergence result, a more complex metamodels requires a more stringent set of assumptions on the distribution of the outer scenario and the inner simulation noise.
In terms of finite-sample behavior, this study provides a comprehensive comparison of different nested simulation procedures, and the findings can be used to guide the choice of a proper nested simulation procedure for a given nested estimation problem.
With extensive numerical experiments, we have found that the finite-sample performance of a procedure can deviate from its theory. 
In theory, supervised learning-based nested simulation procedures often provide higher rates of convergence, but they come at the computational expense of model training and generating predictions from the trained models. 
The likelihood ratio-based procedure requires no training, but it is expensive to compute, and it is also expensive to store the likelihood weights.
As a result, the total computational budget is not necessarily the same as the simulation budget, which is usually a limiting factor for practical applications.
A kernel-based procedure, e.g., \gls{knn} and \gls{var}, requires cross-validation, and its empirical performance depends heavily on the choice of hyperparameters.
A \gls{knn}-based procedure is sensitive to the asset dimension and the problem complexity.
A \gls{krr}-based procedure is computationally expensive, and its cost grows quickly with the simulation budget.
For kernel-based procedures, the computational cost is heavily dependent on the efficient implementation of the associated algorithms.
For a nested estimation problem with a given computational budget, we suggest the use of the regression-based simulation procedure when the budget size is moderate. 
It is efficient to implement, and it exhibits fast empirical convergence in estimating risk measures for popular option portfolios. 
However, we have only examined the performance for option portfolios in this study, where finding a suitable set of basis functions for regression is relatively easy.
In practice, a \gls{va} contract is often high-dimensional in time with a complex payoff structure, and it is a challenging problem for nested simulation procedures.
The time dependence in the feature space leads to multi-collinearity, and the regression-based procedure may not be the best choice in such instances.
In such cases, a neural network-based procedure may be more suitable, as it is a data-driven algorithm that finds a suitable set of basis functions automatically.
In Chapter~\ref{chap:project2}, we examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for \gls{va} contracts.
